Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-30 analysis/paper/paper.qmd
Moved the gis chunk to the results

ggplot() +
  geom_sf(data = veg_forest, aes(fill = veg_forest$Zone)) + #add color for vegetation polygons
  geom_sf(data = pts_forest, aes(color = pts_forest$min_tcsa)) +
  theme_minimal()

ggplot(points_in_veg_zones_forest) +
  aes(Zone,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

summary(aov(min_tcsa ~ as.factor(Zone), points_in_veg_zones_forest))

@@

>>>>

ggplot() +
  geom_sf(data = veg_forest, aes(fill = Zone)) + #add color for vegetation polygons
  geom_sf(data = pts_forest,size = 3, aes(color = min_tcsa)) +
  theme_minimal()

# get rid of zones that has no artifact
points_in_veg_zones_forest_box <- points_in_veg_zones_forest %>% 
  drop_na(Region)

ggplot(points_in_veg_zones_forest_box) +
  aes(Zone,
      min_tcsa) +
  geom_boxplot() +
  geom_quasirandom()

summary(aov(min_tcsa ~ as.factor(Zone), points_in_veg_zones_forest_box))

@@

SPACIAL ANAlysis
@prates2022changes
